\section{Discussion}
Continued experimental and technological improvements have led to a treasure
trove of quantitative biological data [cite], and an ever advancing molecular
view of the constituents that support bacterial growth [cite]. In this work we
have compiled what we believe to be the state-of-the-art knowledge on proteomic
copy number across a broad range of growth conditions in \textit{E. coli}. [We
make the data available through X, interactive Y, and Z]. Through a series of
order-of-magnitude estimates that traverse key steps in the bacterial cell
cycle, this proteomic data has been a resource to guide our understanding of two
key questions: what biological processes limit the absolute speed limit of
bacterial growth, and how do cells alter their  molecular constituents as a
function of changes in growth rate or nutrient availability?
[note what we will discuss broadly?]

For most biological tasks we considered, protein copy numbers were in reasonable
agreement with our order-of-magnitude estimates. Since many of these estimates
represent lower-bound quantities, this suggests that cells do not express
proteins grossly in excess of what is needed for a particular growth rate.
Several exceptions, however, also highlight the dichotomy between a proteome
that appears to maximize growth rate, and one that must also support growth in a
less certain nutrient environment. For carbon uptake, as an example, we find
that cells always express a similar number of glucose transporters irrespective
of growth condition. At the same time, it is interesting to note that many of
the alternative carbon transporter are still expressed in low but non-zero
numbers ($\approx$ 10-100 copies per cell) across growth conditions. This may be
related to the how many of these operons function, which require the initial
presence of the carbon source inside the cell in order to induce expression from
the operon [cite].

[paragraph on physical limits on growth - i.e. volume limit; maybe environmental
conditions like fermentative versus non-fermentive growth]

what biological
processes set the absolute speed limit for how fast bacterial cells can grow and
reproduce


From our analysis we arrive at a ribosome-centric view of growth rate control.
This is in some sense unsurprising  given the long-held observations that
\textit{E. coli} and many other organisms [cite Scott, yeast eLife, others?]
vary their ribosomal abundance as a function of growth conditions and growth
rate. However, through the extensive amount of proteomic data on hand, two key
points also emerge. The first relates to our question of what process sets the
absolute speed limit for how fast bacterial cells can grow.  A bacterium is able
to parallelize many of its processes simply by increasing the number of
transporters and  enzymes.  Even in cases like chromosomal replication, the cell
is not constrained to complete these steps in a single cell doubling, and
instead can perform this over multiple  cell cycles. Ribosomes in contrast are
unique in this regard, since at minimum, they themselves  must at double in
quantity in order for the cell to double it's protein mass. This places an
inherent limit on doubling time that would only be surpased if the cell can
increase the turnover rate of   polypeptide synthesis beyond the apparent limit
of about 17 amino acids per second  or by reducing the number or total size of
the proteins associated with the ribosome. The second relates to the
long-observed correlations between growth rate and cell size
\citep{schaechter1958, si2017}, and between growth rate and ribosomal mass
fraction. While both trends have peaked tremendous curiosity and driven
substantial amounts of research in their own regards, it appears likely that
these relationships are themselves intertwined. In particular, it is the need
for cells to increase their absolute number of ribosomes under conditions of
rapid growth that require cells to also grow in size. 



[paragraph on how this work may be explored further, and specific tests of the model we consider ]

%
%
%
%
% our estimates are
% appear to be in excess of what would be minimally required to support cell
% growth at the observed rates.
%
%
%  to elucidate a
% fundamental question in bacterial physiology -- what sets the speed limit at
% which cells can divide?


%
% Recent years have seen an explosion in our understanding of the cellular
% macromolecular composition at unprecedented resolution. This quantitative,
% molecular view of cell biology has transformed our understanding of how and when
% genes are expressed, to what degree they are expressed, and precisely how they
% are post-translationally modified (a topic we have not considered in this work,
% but appreciate nonetheless). Despite these impressive studies, an understanding
% of how the abundance and regulation is related to growth rate has been largely
% treated with phenomenological models, often containing obscure dimensionless
% parameters or polynomial fits to data. While these phenomenological treatments
% have revealed fascinating features of the resource allocation within the
% proteome, elucidating the molecular details of \textit{how} these resource
% allocation strategies operate has remained enigmatic.
%
% In this work, we present a series of order-of-magnitude estimates to elucidate a
% fundamental question in bacterial physiology -- what sets the speed limit at
% which cells can divide?
%
%
% Countless careers have been built examining the minutiae of each of
% the processes listed in \FIG{categories}, resulting in a treasure
% trove of literature representing decades of careful experimentation, modeling,
% and interpretation of results. Despite the undeniable complexity of each
% individual process, our work illustrates that in order to understand what sets
% the scale of the observed protein copy numbers and their corresponding
% dependence on growth rate, a coarse-grained view of the system is often
% appropriate.
%
%
% [GC: Other topics to discuss include the utility of scrounging the data from the
% literature to assemble, to our knowledge, the most complete view of the
% condition-dependent proteome of \textit{E. coli}.]
%
%
% [Fill in.]

% Parallelized DNA replication represents a solution that allows  \textit{E. coli}
% to synthesize enough rRNA as it grows faster. That the cell appears to
% be synthesizing rRNA near its maximal rate at growth rates above about 0.5 h$^{-1}$
% may also have consequences on robust scaling  between
% cell size and $\langle$\# ori$\rangle$. As one example, when cells are exposed
% to sublethal doses of ribosome-inhibiting drugs like chloramphenicol, there is a
% notable increase in the cell's ribosomal fraction (grey points,
% \FIG{translation_ecoli_partA}(D)), but otherwise the cell is able to maintain
% its cell size according to $\langle$\# ori$\rangle$ \citep{si2017}. While the
% presence of chloramphenicol will inhibit protein synthesis, it will also allow
% for relatively higher rRNA synthesis due to the longer doubling time. If the
% cell can scale it ribosomal protein abundance through feedback from rRNA
% synthesis, than we would expect the relative abundance of ribosomes to increase
% according to the increase in rRNA synthesis. This type of feedback was
% considered long ago \citep{nomura1984} and we consider this possibility further
% in Supplemental Appendix XX.


% While it is difficult to distinguish between causality and correlation, the data
% also helps us resolve why cell size, should exhibit an exponential increase with growth
% rate once cells begin to parallelize DNA replication. Specifically,
%
% is consistent with the need for cells to increase their effective rRNA gene
% dosage in order to grow according to the constraint set by Equation 2. Importantly, it
% may also shed some light on the notable increase in ribosomal content
% that is observed when sublethal doses of antibiotics \citep{scott2010, dai2016}.
% Specifically, if rRNA synthesis is rate limiting, and nutrient conditions
% largely dictate the extent of overlapping DNA replication cycles, than addition
% of antibiotic will lengthen the doubling time and allow increased rRNA
% synthesis relative to the rate of cell division. In Supplemental Section XX, we
% consider this further using additional data from \cite{si2017}.


% A number of recent papers further highlight the possibility that regulation
% (p)ppGpp may be the critical component of the apparent scaling laws in
% \textit{E. coli}. In the context of ribosomal activity, increased levels of
% (p)ppGpp are associated with lower ribsomal content, and at slow growth
% are associated with reduced activity by ribosomes and RNA polymerse \citep{dai2016,
% dai2018} [citations for RNAP]. Titration of the cellular (p)ppGpp concetrations (up or down) can
% invoke similar proteomic changes reminiscent of those observed under nutrient
% limitation \citep{zhu2019}. In light of the limiting dependence of ribosome copy
% number on chromosomal gene dosage, it was recently shown that growth in a
% (p)ppGpp null strain abolishes both the scaling in cell size  and the
% $\langle$\# ori$\rangle$ / $\langle$\# ter$\rangle$ ratio. Instead, cells
% exhibited a high $\langle$\# ori$\rangle$ / $\langle$\# ter$\rangle$ closer to 4
% and cell size more consistent with a fast growth state where (p)ppGpp levels are
% low \citep{fernandezcoll2020}. From these results, perhaps the perspective to
% take is that the scaling laws  reflect an attempt for the cell to mitigate its
% biological activity according  to available nutrients.
